Data preparation

### 2020-05-29 docs/paper.Rmd
Ttitulos
Se eliminan simbolos = en titulos.
Se eliminan las cosas del repo merit-scale

To be submitted in Social Indicators Research
Ideas: meritocracy and redistributive
To what extent perceptions of meritocracy affect redistributive preferences? The argument is that
if individuals and groups in general consider that merit leads to career advancement and to move
upwards in the status ladder, a possible consequence is that redistribution from the side of the
cental agency as the state could be less supported as individuals are seen as responsible for their
own fate. In this sense, perceptions of a well-functioning meritocracy would be linked to less
redistributive preferences. Many ad-hoc decisions in operationalization and building instruments.
Some of them represent different research interests and this is valid, but in many cases they are
not well argued and are actually wrong. Of course this is probably not only the case for studying
meritocratic beliefs, but this can be used both for researchers studying specifically this topic and
jcastillov@uc.cl - jc-castillo.com
1
others that deal with measurement issues in international comparisons. Validity of measures in
cross-national research ... is not really "up to date", mostly in sociology. Restricted to survey research,
mostly comparative. Conceptual clarification: meritocratic pereceptions and meritocratic
preferences. Beliefs, although mostly linked with normative principles, sometimes they are also
used of perceptions (Reynolds and Xian, 2014), or even somentime "justice perceptions", which is
something ambiguous as justice, as a normative ideal, cannot really be perceived and mostly refer
to perception of inequality (which is not necessarily consider unjust).
One: definition of meritocracy and conceptual framework Two: measurement of meritocratic
perceptions (merit and non-merit)
1.1 Measuring meritocratic perceptions and beliefs ... maybe a different
paper- Mau seminar presentation
From a sociological perspective, the study of meritocracy can be framed in the area of distributive
or social justice studies, which in broad terms empirical research on justice "deals solely with
empirical phenomena, concentrating on the empirical validity of conceptions of justice for individuals’
attitudes and behavior and for the structure and processes of society or other forms of
social aggregation" (Liebig and Sauer, 2016, p.37). Within this framework, beliefs about inequality
through survey research is an area of studies that was first conceptualized as such by Kluegel
and Smith (1981) and that has developed mainly through comparative studies as the ISJP and
the ISSP.

>>>>

To be submitted in Social Indicators Research
Ideas: meritocracy and redistributive
To what extent perceptions of meritocracy affect redistributive preferences? The argument is that
if individuals and groups in general consider that merit leads to career advancement and to move
upwards in the status ladder, a possible consequence is that redistribution from the side of the
cental agency as the state could be less supported as individuals are seen as responsible for their
own fate. In this sense, perceptions of a well-functioning meritocracy would be linked to less
redistributive preferences. Many ad-hoc decisions in operationalization and building instruments.
Some of them represent different research interests and this is valid, but in many cases they are
not well argued and are actually wrong. Of course this is probably not only the case for studying
meritocratic beliefs, but this can be used both for researchers studying specifically this topic and
jcastillov@uc.cl - jc-castillo.com
1
others that deal with measurement issues in international comparisons. Validity of measures in
cross-national research ... is not really "up to date", mostly in sociology. Restricted to survey research,
mostly comparative. Conceptual clarification: meritocratic pereceptions and meritocratic
preferences. Beliefs, although mostly linked with normative principles, sometimes they are also
used of perceptions (Reynolds and Xian, 2014), or even somentime "justice perceptions", which is
something ambiguous as justice, as a normative ideal, cannot really be perceived and mostly refer
to perception of inequality (which is not necessarily consider unjust).
One: definition of meritocracy and conceptual framework Two: measurement of meritocratic
perceptions (merit and non-merit)
1.1 Measuring meritocratic perceptions and beliefs ... maybe a different
paper- Mau seminar presentation
From a sociological perspective, the study of meritocracy can be framed in the area of distributive
or social justice studies, which in broad terms empirical research on justice "deals solely with
empirical phenomena, concentrating on the empirical validity of conceptions of justice for individuals’
attitudes and behavior and for the structure and processes of society or other forms of
social aggregation" (Liebig and Sauer, 2016, p.37). Within this framework, beliefs about inequality
through survey research is an area of studies that was first conceptualized as such by Kluegel
and Smith (1981) and that has developed mainly through comparative studies as the ISJP and
the ISSP.

### 2020-05-29 production/prod_analysis-cfa.rmd
Ttitulos
Se eliminan simbolos = en titulos.
Se eliminan las cosas del repo merit-scale

```{r}
# 2.3 Measurement structure ------------- ########

@@

###	################## 	agregar un sumary mas  reducido

@@

	# Categorical	  
		fit_red1c <- cfa(cfa_red1,data=redistrib, 
			ordered = c("income_dif","unemployed","taxes", "health", 
			"educ")) 
	#	summary(fit_red1c, fit.measures=TRUE,standardized=TRUE)
###	################## 	                                         agregar un sumary mas  reducido

@@

```{r}
# 5.2 Descriptives ---------------------- #####
	load("input/data/proc/pref.rda")

@@

```{r}
# 5.3 Models ---------------------------- ######

@@

# Multilevel (with factor scores) ################################## No funciono nada de este apartado. 
	# check simple regresion
	#ols_prefred=lm(redist ~ univ + quintile + sstatus + gini_market)
	# summary(ols_prefred) # ok, similar SEM, scores OK

@@

# 6. MODELS C: MERITOCRACY ================ =

@@

# 6.2 Descriptives ---------------------- #####

@@

    ################################agregar Polichoric.
    # Macro level corr

@@

```{r results='asis' , message= F}
# 6.3 Models -----------------------------#####

>>>>

```{r}
# 2.3 Measurement structure

@@

@@

	# Categorical	  
		fit_red1c <- cfa(cfa_red1,data=redistrib, 
			ordered = c("income_dif","unemployed","taxes", "health", 
			"educ")) 
	#	summary(fit_red1c, fit.measures=TRUE,standardized=TRUE)
#

@@

```{r}
# 5.2 Descriptives 
	load("input/data/proc/pref.rda")

@@

```{r}
# 5.3 Models

@@

# Multilevel (with factor scores) #No funciono nada de este apartado. 
	# check simple regresion
	#ols_prefred=lm(redist ~ univ + quintile + sstatus + gini_market)
	# summary(ols_prefred) # ok, similar SEM, scores OK

@@

# 6. MODELS C: MERITOCRACY

@@

# 6.2 Descriptives

@@

    # agregar Polichoric.
    # Macro level corr

@@

```{r results='asis' , message= F}
# 6.3 Models

### 2020-05-29 production/prod_prep-data-A.rmd
Ttitulos
Se eliminan simbolos = en titulos.
Se eliminan las cosas del repo merit-scale

# 1.MEASUREMENT MERIT & GETTING AHEAD

#Note: object now generated from different
#script (merit_per_pref.R; merit_per_pref.rda)

# 2. MEASUREMENT REDISTRIBUTION

# 2.1 Data preparation, gen redistrib.rda

@@

```{r}
  # Rename & define object
    names(issp2009)  
    redistrib=issp2009[,c("v5","v33","v34","v36","v38","v39","id")] 
    redistrib$income_dif= redistrib$v33
    redistrib$unemployed= redistrib$v34
    redistrib$taxes     = redistrib$v36
    redistrib$health    = redistrib$v38
    redistrib$educ      = redistrib$v39

    names(redistrib)
    redistrib=redistrib[-c(2:6)]
    stargazer(redistrib[-c(1,2)], type="html")

@@

```{r}
# 2.5 Invariance -------------pendiente-- -----
    # measurementInvariance(cfa_2, data = redistrib, group = "v5")      # No funciono la invarianza arreglar.

@@

# End sec 2; saved objects
	  # redistrib.rda: clean & recoded
	  # redistrib_sco.rda : fac scores [por ahora en analysis]

# 3.PREP INDIVIDUAL & MACRO VAR

# 3.1 Individual level variables 
```{r}
  indepvar=issp2009
	summary(indepvar$id)
	length(indepvar$id)

@@

	    # Recode missings
	     	names(indepvar)
	    	freq(indepvar$cl_inc)
	    	summary(indepvar[182:222]) # missings vary (note 2)

@@

# 3.2 Indep macro var ------------------- ####
```{r}

	# Inequality swiid (4)        #########################3 No encuentro el objeto. 
	swiid =	read_stata("input/data/original/swiid8_2.dta")

@@

# 5.1 Data preparation - pref.rda ------- #####

@@

```{r}
# 6.1 Data preparation - meritocracy.rda  #####

>>>>

# Measurement Merit & Getting ahead

Note: object now generated from different
script (merit_per_pref.R; merit_per_pref.rda)

#  Measurement and Redistribution

## Data preparation, gen redistrib.rda

@@

```{r}
  # Rename & define object
    #names(issp2009)  
    redistrib=issp2009[,c("v5","v33","v34","v36","v38","v39","id")] 
    redistrib$income_dif= redistrib$v33
    redistrib$unemployed= redistrib$v34
    redistrib$taxes     = redistrib$v36
    redistrib$health    = redistrib$v38
    redistrib$educ      = redistrib$v39

    #names(redistrib)
    redistrib=redistrib[-c(2:6)]
    stargazer(redistrib[-c(1,2)], type="html")

@@

```{r}
# 2.5 Invariance
    # measurementInvariance(cfa_2, data = redistrib, group = "v5")      # No funciono la invarianza arreglar.

@@

 End sec 2; saved objects
	  # redistrib.rda: clean & recoded
	  # redistrib_sco.rda : fac scores [por ahora en analysis]

# Preparation Individual & Macro variables.

## Individual level variables 
```{r}
  indepvar=issp2009
	summary(indepvar$id)
	length(indepvar$id)

@@

	    # Recode missings
	     	#names(indepvar)
	    	freq(indepvar$cl_inc)
	    	summary(indepvar[182:222]) # missings vary (note 2)

@@

# 3.2 Indep macro var 
```{r}

	# Inequality swiid (4)         
	swiid =	read_stata("input/data/original/swiid8_2.dta")

@@

# 5.1 Data preparation

@@

```{r}
# 6.1 Data preparation - meritocracy.rda
